Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-08-26 Thesis/abstract.qmd
fill in acknowledgement

```{r}
#| message: false
#| echo: false
library(tidyverse)
library(knitr)
library(kableExtra)
dt <- tribble(
  ~`Chapter`, ~`Publication title`, ~Status, ~`Student contribution`, ~`Co-authors contribution`, ~`Coauthors are Monash students`,
  2, "A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol", "Published in the Journal of Computational and Graphical Statistics", "80%  Concept, Analysis, Software, Writing", "D. Cook 10%,  \n E. Tanaka 5%, \n S. VanderPlas 5%", "No"
  # 3, "Automated Assessment of Residual Plots with Computer Vision Models", "Unsubmitted", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n P. Menéndez 5%, \n U. Laa 2.5%,  \n N. Langrené 2.5%", "No",
  # 4, "Software for Automated Residual Plot Assessment: autovi and autovi.web", "The R package autovi on CRAN", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n E. Tanaka 5%, \n S. VanderPlas 2.5%, K. Ackermann 2.5%", "No"
)

@@

Chapter 3, *Automated Assessment of Residual Plots with Computer Vision Models*, and Chapter 4, *Software for Automated Residual Plot Assessment: autovi and autovi.web*, are planned for submission to peer-reviewed journals in the near future.

>>>>

```{r}
#| message: false
#| echo: false
library(tidyverse)
library(knitr)
library(kableExtra)
dt <- tribble(
  ~`Chapter`, ~`Publication title`, ~Status, ~`Student contribution`, ~`Co-authors contribution`, ~`Coauthors are Monash students`,
  2, "A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol", "Published in the Journal of Computational and Graphical Statistics", "80%  Concept, Analysis, Software, Writing", "D. Cook 10%,  \n E. Tanaka 5%, \n S. VanderPlas 5%", "No",
  3, "Automated Assessment of Residual Plots with Computer Vision Models", "To be submitted", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n P. Menéndez 5%, \n U. Laa 2.5%,  \n N. Langrené 2.5%", "No",
  4, "Software for Automated Residual Plot Assessment: autovi and autovi.web", "To be submitted", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n E. Tanaka 5%, \n S. VanderPlas 2.5%, K. Ackermann 2.5%", "No"
)

@@
